Inference of Gravitational Lens Time Delays Using Gaussian Processes

### 2013-04-22 doc/Leon/ms.tex
More work on the table

% Every Latex document starts with a documentclass command
\documentclass[a4paper, 11pt]{article}

@@

\begin{table}[h!]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Parameter & Description & Prior\\
\hline
$\{m_k\}$ & Mean magnitudes for each image & Uniform$(m_{\rm min}, m_{\rm max})$\\
$\{\tau_k\}$ & Time delays for each image & Cauchy$(0, \tau_{\rm range}/10)T(\tau_{\rm min}, \tau_{\rm max})$\\
\end{tabular}
\end{center}
\end{table}

>>>>

% Every Latex document starts with a documentclass command
\documentclass[a4paper, 10pt]{article}

@@

\begin{table}[h!]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Parameter & Description & Prior\\
\hline
$\{m_k\}$ & Mean magnitudes & Uniform$(m_{\rm min}, m_{\rm max})$\\
$\{\tau_k\}$ & Time delays & Cauchy$(0, \tau_{\rm range}/10)T(\tau_{\rm min}, \tau_{\rm max})$\\
$\{\sigma_{\rm ML}\}$ & Standard deviations of microlensing signals & LogUniform$()$\\
$\{L_{\rm ML}\}$ & Timescales of microlensing signals & LogUniform$()$\\
$\alpha$ & Smoothness parameter for microlensing signals & Uniform$(1,2)$\\
$\sigma_{\rm QSO}$ & Standard deviation of quasar variability & LogUniform$()$\\
$L_{\rm QSO}$ & Timescale of quasar variability & LogUniform$()$\\
$f_{\rm bad}$ & Fraction of data points with incorrect errorbars & Uniform$(0,1)$\\
$K$ & Boost factor for bad errorbars & LogUniform$(1, 100)$\\
$\{b_i\}$ & Flag for whether each errorbar is bad & Bernoulli$(f_{\rm bad})$\\
\hline
\end{tabular}
\end{center}
\end{table}
